Lattice Boltzmann study of mass transfer for complicated geometries

### 2012-01-06 Text/introduction.tex
Need to keep the same Peclet number either with periodic boundary conditions (easiest case). Calculate critical velocities.

The solver was through consequent steps. First, we extracted the velocity profiles from the original binary-liquid simulations. Then, we imposed walls with velocity of the bubble, so the bubble stays still. At the surface of the bubble the free boundary conditions were imposed, see \ref{appendix-free-surface}. One of the examples is shown in Fig. \ref{fig:streamlines:tweaked:velocity}.
\begin{figure}
\includegraphics[width=\textwidth]{Figures/original.eps}\\
\includegraphics[width=\textwidth]{Figures/performed.eps}\\
\caption{The comparison between original velocity fields and velocity fields obtained from free surface solver. \label{fig:streamlines:tweaked:velocity}}
\end{figure}

This section does the job of increasing velocity results. The ulimate goal is to increase velocity
to about $20-50$ times for velocity while keeping dimensionless parameters the same. The
nondimensional parameter Peclet number governs the advection-diffusion equation:
\beq
Pe=\frac{U_{bubble} N_y}{D},
\feq
where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
means one needs to increase the diffusion coefficient as well. We make a few runs with velocities
$5,10,20,40$ times larger than original velocities.

\appendix
\section{Free surface boundary conditions}
There are a few implementations of free boundary conditions \cite{ginzburg-free,verberg-free}. However, we developed the easy solver to impose the free surface boundary conditions at the complicated surface of the bubble. The reason is to impose the symmetric boundary conditions. Because the boundary is the staircase approximation, one can find the normal to the boundary which is always located by the angle of multiple of $45$, see Fig. \ref{fig:free:surface}. Imposing the symmetric boundary conditions requires $U_{n,F}$=$U_{n,B}$ and $U_{\tau,F}=U_{\tau,B}$. We can copy populations in the certain order to do it, for example $f_{B,i}=f_{F,\bar{i}}$, where $c_i$ and $c_{\bar{i}}$ are complementary directions, where $c_{i,n}=-c_{\bar{i},n}$ and $c_{i,\tau}=c_{\bar{i},\tau}$, where $c_{i,n}=(\bm{c_i} \cdot \bm{n})\bm{n}$ and $c_{i,\tau}=\bm{c_i}-(\bm{c_i}\cdot \bm{n})\bm{n}$.

>>>>

The solver was through consequent steps. First, we extracted the velocity profiles from the
original binary-liquid simulations. Then, we imposed walls with velocity of the bubble, so the
bubble stays still. At the surface of the bubble the free boundary conditions were imposed, see
\ref{appendix-free-surface}. One of the examples is shown in Fig.
\ref{fig:streamlines:tweaked:velocity}. Among all the simulations the bulk velocity in film and the
slug are different of no more than $7$ percent. {\color{red} Add some pictures froms streamlines.py
if it's required to show more.}
\begin{figure}
\includegraphics[angle=90,width=\textwidth]{Figures/original.eps}\\
\includegraphics[angle=90,width=\textwidth]{Figures/performed.eps}\\
\caption{The comparison between original velocity fields and velocity fields obtained from free surface solver. \label{fig:streamlines:tweaked:velocity}}
\end{figure}

\section{Keeping Peclet}
This section does the job of increasing velocity results. The ulimate goal is to increase velocity
to about $20-50$ times for velocity while keeping dimensionless parameters the same. The
nondimensional parameter Peclet number governs the advection-diffusion equation:
\beq
Pe=\frac{U_{bubble} N_y}{D},
\feq
where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
means one needs to increase the diffusion coefficient as well. We make a few runs with velocities
$5,10,20,40$ times larger than original velocities.

\appendix
\section{Free surface boundary conditions}
\label{appendix-free-surface}
There are a few implementations of free boundary conditions \cite{ginzburg-free,verberg-free}.
However, we developed the easy solver to impose the free surface boundary conditions at the
complicated surface of the bubble. The reason is to impose the symmetric boundary conditions.
Because the boundary is the staircase approximation, one can find the normal to the boundary which
is always located by the angle of multiple of $45$, see Fig. \ref{fig:free:surface}. Imposing the
symmetric boundary conditions requires $U_{n,F}$=$U_{n,B}$ and $U_{\tau,F}=U_{\tau,B}$. We can copy
populations in the certain order to do it, for example $f_{B,i}=f_{F,\bar{i}}$, where $c_i$ and
$c_{\bar{i}}$ are complementary directions, where $c_{i,n}=-c_{\bar{i},n}$ and
$c_{i,\tau}=c_{\bar{i},\tau}$, where $c_{i,n}=(\bm{c_i} \cdot \bm{n})\bm{n}$ and
$c_{i,\tau}=\bm{c_i}-(\bm{c_i}\cdot \bm{n})\bm{n}$.
